---
title: "data trivia"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{data_trivia}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Data trivia

Let's setup our environment.

```{r, eval = FALSE}
library(meteobr)
```


## Meteorological data

```{r, eval = FALSE}
df = get_data(first.day = "2001-01-01", last.day = "2001-01-02", vars = c("wind_burst", "temperature_air", "humidity"))
head(df)
```

Bellow is the description of the variables you can access through `get_data()` and `get_inmet_data_by_year()`. The time variable refers to the hour marked +1 hr. So, if its written that

````{verbatim}
time            station   temperature_max   humidity
<chr>           <chr>               <dbl>      <dbl>
2001/01/01 00   A001                 20.7         93
2001/01/01 01   A001                 20           95
````

it means that the maximum temperature at the station A001 on the day 2001-jan-01 between 00:00 and 01:00 UTC was 20.7 degrees Celsius. It's also true that - on the same day and at the same station - 20 °C was the maximum temperature between 01:00 and 02:00 UTC. In a nutshell: if you want to check data that refers to some day in hours between 11:00 and 13:59 UTC, you'll need to filter the hours 11, 12 and 13. See variables descriptions bellow:


| Column name            | Original name                                          | Unity      |
|------------------------|--------------------------------------------------------|------------|
| `time`                 | ****                                                   | UTC hour   |
| `station`              | ****                                                   | station.id |
| `precipitation`        | PRECIPITAÇÃO TOTAL, HORÁRIO (mm)                       | mm         |
| `atm_pressure`         | PRESSAO ATMOSFERICA AO NIVEL DA ESTACAO, HORARIA (mB)  | mB         |
| `atm_pressure_max`     | PRESSÃO ATMOSFERICA MAX.NA HORA ANT. (AUT) (mB)        | mB         |
| `atm_pressure_min`     | PRESSÃO ATMOSFERICA MIN. NA HORA ANT. (AUT) (mB)       | mB         |
| `radiation`            | RADIACAO GLOBAL (Kj/m²)                                | Kj/m²      |
| `temperature_air`      | TEMPERATURA DO AR - BULBO SECO, HORARIA (°C)           | °C         |
| `temperature_dew`      | TEMPERATURA DO PONTO DE ORVALHO (°C)                   | °C         |
| `temperature_max`      | TEMPERATURA MÁXIMA NA HORA ANT. (AUT) (°C)             | °C         |
| `temperature_min`      | TEMPERATURA MÍNIMA NA HORA ANT. (AUT) (°C)             | °C         |
| `temperature_dew_max`  | TEMPERATURA ORVALHO MAX. NA HORA ANT. (AUT) (°C)       | °C         |
| `temperature_dew_min`  | TEMPERATURA ORVALHO MIN. NA HORA ANT. (AUT) (°C)       | °C         |
| `humidity_max`         | UMIDADE REL. MAX. NA HORA ANT. (AUT) (%)               | %          |
| `humidity_min`         | UMIDADE REL. MIN. NA HORA ANT. (AUT) (%)               | %          |
| `humidity`             | UMIDADE RELATIVA DO AR, HORARIA (%)                    | %          |
| `wind_direction`       | VENTO, DIREÇÃO HORARIA (gr) (° (gr))                   | ° (dgr)    |
| `wind_burst_max`       | VENTO, RAJADA MAXIMA (m/s)                             | m/s        |
| `wind_burst`           | VENTO, VELOCIDADE HORARIA (m/s)                        | m/s        |


## Stations data

```{r, eval = FALSE}
head(stations)
```

The data set `stations` contains data about INMET's automatic stations. See variables descriptions bellow:

| Column         | Description                                                |
|----------------|------------------------------------------------------------|
| `station.id`   | INMET's id of the station                                  |
| `station.name` | original name of the station on INMET's website            |
| `town.id`      | IBGE code for station's town                               |
| `town.name`    | name of the town in which station is located, standardized |
| `state`        | state in which the station is located (abbreviation)       |
| `region`       | national region in which the station is located            |
| `lat`          | latitude of the station (meters)                           |
| `lon`          | longitude of the station (meters)                          |
| `alt`          | altitude of the station (meters)                           |
