---
title: "example"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Example

First, call the package.

```{r, eval = FALSE}
library(meteobr)
```

Now, let's talk business.

## Downloading data

Suppose you've just installed `meteobr` and it's your interest to deal with data about humidity and radiation between june-2003 & august-2005. You already checked the [vignette data trivia](data-trivia.html) and you know that the columns you're interested in are `humidity` and `radiation`.

The first step is to download the treated data. Unfortunately you can't have very large data sets easily available (through the [`data/` folder](https://r-pkgs.org/data.html)). Our solution to that was to let the user download the data 'à la carte'; this is done with the function `set_data_locally()`.


```{r, eval = FALSE}
# The code bellow downloads only the data between 2003 & 2005
set_data_locally(2003:2005)

# The code bellow downloads all data available
set_data_locally()

```

Even though you just want to analyse the years 2003-2005, we recommend that you download all available data. That's better because it makes it easier to run future analysis without having to wait your internet connection. Note that all data is less than 900 Mb. Besides that, running the default `set_data_locally()` right away will let you know if there is any error in the data download/storage process.

Talking about that, it's worth mentioning the following:

* You should only download data once. If you do 
  
  ```{r, eval = FALSE}
  year = 2010
  
  # 1
  set_data_locally(year)
  
  # 2
  set_data_locally(year)
  
  ```

  the first line will actually download the data, and the second line will simply note that the data is already there.

* You shouldn't modify the `.Rdata` files by hand. If you do so, it's likely that the same data will be downloaded again, and the program will overwrite it.

* If you're having any problem with this process, you can verify if the data is stored where it's supposed to be - with the function `local_data()`. It returns the folder (in your machine) where the data is stored. You can 'set the data locally' yourself by downloading everything that is in our [GitHub data repo](https://github.com/carlosdemoura/meteobr/tree/master/data/repo) and copying it to the `local_data()` folder.

  ```{r, eval = FALSE}
  local_data()
  ```

* The function `set_data_locally()` in called by the function `get_data()` (which we'll talk next), so it's perfectly possible to use our package without having to call `set_data_locally()`.


## Geting the data

Now that the data is readily available, let's get it! Well, not us, the function `get_data()`. `first.day` & `last.day` must be in the format yyyy-mm-dd, the columns we want are in `vars` and, as we want data across all stations, `stations` is set to NULL (in this case, there was no need to even pass this argument).

```{r, eval = FALSE}
df = get_data(first.day = "2003-06-01",
              last.day  = "2005-08-31",
              vars = c("humidity", "radiation"),
              stations = NULL)

dplyr::glimpse(df)
```

Ta-dah!

## Wider data

Let's say we need our data to be in the wider format. Since this isn't possible with two variables (?), lets get another data. Let's say we're interested in the maximum temperature between 10 and 11 hours UTC. The code below filters and turn the data into the wider format.

```{r, eval = FALSE}
library(tidyverse)
library(lubridate)
library(purrr)

df_long = get_data(first.day = "2003-01-01",
                   last.day  = "2003-01-31",
                   vars = "temperature_max") %>%
  mutate(hour = sapply(time, function(x) {x |> strsplit(" ") |> pluck(1) |> pluck(2) |> as.numeric()} )) %>%
  filter(hour == 10) %>%
  select(!hour)
  
glimpse(df_long)

df_wide = df_long %>%
  mutate(time = as_factor(time)) %>%
  pivot_wider(names_from = time, values_from = temperature_max) %>%
  as_tibble()

head(df_wide)
```


## If everything goes wrong

If everything above goes wrong ~~I should retire~~ you can still use `get_inmet_data_by_year()` and then `rbind()` the data sets. The downside of this approach is that this function downloads and processes the original raw data every time it's called, which is time consuming.

Bellow we have a way to get the same data as before, under this new approach.

```{r, eval = FALSE}
vars = c("humidity", "radiation")

df2003 = get_inmet_data_by_year(2003, first.day = "06-01", last.day = "12-31", vars = vars)
df2004 = get_inmet_data_by_year(2004, vars = vars)
df2005 = get_inmet_data_by_year(2005, first.day = "01-01", last.day = "08-31", vars = vars)

df = rbind(df2003, df2004, df2005)
glimpse(df)
```
